\begin{recipe}{Paella}{}{}
\ing[3]{Tbsp}{olive or grapeseed oil}
Heat a 12-inch (or larger) heavy saut\'{e} or paella pan until a bead of water
skitters and evaporates. Add oil and heat until wavy.

\ing[1]{cup}{kielbasa, cut into slices and quartered}
Add kielbasa and saut\'{e} until it starts to brown.

\ing[3]{cloves}{garlic}
\ing[1]{cup}{onions, diced}
\ing[1]{cup}{bell peppers, diced}
Saut\'{e} garlic, onions, and peppers, stirring until garlic and onions turn
golden.

\ing[2]{cups}{long-grain white rice}
\ing[2]{}{boneless chicken thighs, cut into strips}
Add rice and chicken strips and saut\'{e} until chicken no longer looks pink
and the edges of the rice become translucent.

\ing[\fr14]{cup}{dry white wine}
\ing[1\fr14]{cup}{chicken broth}
\ing[1]{cup}{diced canned tomatoes with juice}
\ing[\fr18]{tsp}{crumbled saffron}
\ing[\fr12]{tsp}{dried thyme}
\ing[2]{tsp}{smoked paprika}
\ing[]{pinch}{cayenne}
Add wine, broth, tomatoes, saffron, thyme, paprika, and cayenne. Cook, covered
and undisturbed, over medium heat until most of the liquid gets absorbed (~13
minutes).

\ing[20]{frozen}{shrimp, raw \& cleaned}
\ing[1\fr14]{pound}{hard-shelled clams and/or mussels, scrubbed}
\ing[1]{cup}{peas}
\ing[\fr12]{cup}{sliced pimento-stuffed green olives}
Stir in shrimp, clams/mussels, peas, and olives. Cook, covered, until shellfish
open wide and shrimp turn pink (~5 minutes). Discard any unopened
shellfish.\newstep

Check doneness of the rice (it will cook a little more while it sits).\newstep

Remove from heat and let stand, covered, until all liquid gets absorbed (~5
minutes).

\freeform If, during the 15 minutes, the liquid runs out, simply add more
chicken broth or wine.

\end{recipe}
